---
title: "Projects!"
---

```{r echo=FALSE,message=FALSE, warning=FALSE}
library(tidyverse)
library(ggplot2)
library(here)
library(flextable)
library(janitor)
library(readxl)
```

# Personal Hydration Data

The last three years I have noticed that I liked the water at my workplace at lot more than other water available to me which led me to track my intake in ounces for this study! Every day for the past few weeks I have collected the amount of water consumed throughout the day based on the primary independent variable of whether or not I worked.

```{r echo=FALSE, message=FALSE, warning=FALSE}
#name hydration data

hydrationdata <- read.csv ("SM 193DS - Sheet1.csv")


#clean data to all lower case and no spaces
hydration_clean <- hydrationdata |>
  rename(
    water_intake_oz = "water.intake..oz.",
    work_day = "work.day"
  ) |> 
  select(Date, water_intake_oz, work_day) |>
  mutate(
    work_day= tolower(trimws(work_day)),
    water_intake_oz= as.numeric(water_intake_oz)
  )

mean_water_intake <- hydration_clean |>
  group_by(work_day) |>
  summarise(mean_intake= mean(water_intake_oz, na.rm = TRUE))

#make boxplot with. work day and water intake in pink and green
boxplot(water_intake_oz ~ work_day, 
        data = hydration_clean,
        main = "Water Intake by Work Day",
        xlab = "Work Day",
        ylab = "Water Intake (oz)",
        col = c("lightpink", "lightgreen")) 

#made a caption for the boxplot
mtext("Figure 1: boxplot comparing mean water intake between work days and nonwork days ",
      side=1, line=4.1, cex= 0.9, col = "black")
```

```{r echo=FALSE, message=FALSE, warning=FALSE}
#made time plot but had to rename 
hydration_clean$Date <- as.Date(hydration_clean$Date)


plot(hydration_clean$Date, hydration_clean$water_intake_oz,
     type = "l", col = "blue", lwd = 2,
     xlab = "Date", ylab = "Water Intake (oz)",
     main = "Daily Water Intake Over Time")

mtext("Figure 2: graph over time on the amount of water consumed",
      side=1, line=4.2, cex= 0.9, col = "black")


```

```{r echo=FALSE, message=FALSE, warning=FALSE}
flextable(mean_water_intake)

```

# RO water spots at UCSB
